
\item If $R$ is the range of  a projectile on a horizontal plane and $h$ its maximum height, then maximum horizontal range with the same speed of projection is :
\begin{tasks}(2)
\task $2h$
\task $\dfrac{R^2}{8h}$
\task $2R + \dfrac{h^2}{8R}$
\task $2h + \dfrac{R^2}{8h}$\ans
\end{tasks}

\item An object is thrown horizontally from a tower $H$ meter high with a velocity of $\sqrt{2gH} m/s$. Its speed on striking the ground will be :
\begin{tasks}(2)
\task $\sqrt{2gH}$
\task $\sqrt{6gH}$
\task $2\sqrt{gH}$\ans
\task $2\sqrt{2gH}$
\end{tasks}

\item Two bullets are fired at angles $\theta$ and  $90^\circ -\theta$, the ratio of their time of flights is:
\begin{tasks}(2)
\task $1 : 1$
\task $\tan \theta : 1$\ans
\task $1 : \tan \theta$
\task $\tan^2 \theta : 1$
\end{tasks}

\item A particle is projected from a point $O$ with a velocity $u$ in a direction making an angle $\alpha$ upward with the horizontal. At $P$ it is moving at right angles to its initial direction. Its velocity at $P$ is :
\begin{tasks}(2)
\task $u\tan \alpha$
\task $u\cot \alpha$\ans
\task $u \cosec \alpha$
\task $u\sec \alpha$
\end{tasks}



\item Suppose a player hits several baseballs. Which baseballs will be in the air for the longest time?
\begin{tasks}
\task The one with the farthest range.
\task The one which reaches maximum height.\ans
\task The one with the greatest initial velocity.
\task The one leaving the bat at $45^\circ$ with respect to the ground.
\end{tasks}

\item The velocity at the maximum height of a projectile is half of its initial velocity of projection. If magnitude of initial velocity is $u$, its range on the horizontal plane is :
\begin{tasks}(2)
\task $\dfrac{\sqrt{3}u^2}{2g}$\ans
\task $\dfrac{u^2}{2g}$
\task $\dfrac{3u^2}{2g}$
\task $\dfrac{3u^2}{g}$
\end{tasks}



\item A projectile is fired with a velocity $u$ making an angle $\theta$ with the horizontal. What is the magnitude of change in velocity when it is at the highest point?
\begin{tasks}(2)
\task $u\cos \theta$
\task $u$
\task $u\sin \theta$\ans
\task $u\cos \theta -u$
\end{tasks}
